Synthesizing Symmetric Lenses

### 2018-07-12 papers/SymmetricLenses/main.tex
more space tweaks

\GreedySeqSynth then loops until there are no more atom lenses in the priority
queue. Within the loop, a popped atom lens is considered 
``useful'' if adding it to the sequence will lower the
cost of the generated sequence lens, or if examples show that one of its atoms
must not be disconnected. Each atom can be part of only one lens at a time, so
the algorithm must sometimes a previously chosen atom lens in order to connect an
atom that must not be disconnected.
After all atoms have been popped, the sequence lens is validated and
returned. The algorithm succeeds when all atoms that must not be disconnected
are involved in an atom lens, but \PCF{SLensBuilder.ToDNFLens}
returns \None otherwise.

@@

\paragraph*{Expansion Inference} These additional rewrites make the search
through possible regular expressions much harder. Our algorithm automatically
will identify when certain closed regular expressions can \emph{only} be
involved in a disconnect lens.  Such regular expressions will automatically be
opened.

>>>>

\GreedySeqSynth loops until there are no more atom lenses in the priority
queue. In the loop, a popped atom lens is considered 
``useful'' if adding it to the sequence will lower the
cost of the generated sequence lens, or if examples show that one of its atoms
must not be disconnected. Each atom can be part of only one lens at a time, so
the algorithm must sometimes remove a previously chosen atom lens in order to connect 
one that must not be disconnected.
% After all atoms have been popped, the sequence lens is validated and
% returned.
The algorithm succeeds when all atoms that must not be disconnected
are involved in an atom lens; \PCF{SLensBuilder.ToDNFLens}
returns \None otherwise.

@@

\paragraph*{Expansion Inference} These additional rewrites make the search
through possible regular expressions harder. Our algorithm 
identifies when certain closed regular expressions can \emph{only} be
involved in a disconnect lens.  Such regular expressions will automatically be
opened.
